Data Specialization for a Staged Lambda Calculus

### 2015-02-27 paper/implementation.tex
eliminate inconsistent uses of 'part'ition

We allow staging annotations around declarations. For example,
\begin{lstlisting}
3`atsigngrnd{`1`
  datatype list = Empty | Cons of int * list
  fun part (...) = ...
`3`}`1`
fun qsStaged (...) = ...`
\end{lstlisting}
declares the \texttt{list} datatype and \texttt{part} function at world \bbonep,
by elaborating into:
\begin{lstlisting}
1`val 3`grnd{`Empty3`}` = 3`grnd{`roll (inj ...)3`}`
val 3`grnd{`Cons3`}`  = 3`grnd{`fn (...) => roll (inj ...)3`}`
val 3`grnd{`part3`}`  = 3`grnd{`fn (...) => ...3`}`
val qsStaged    = fn (...) => ...`
\end{lstlisting}

>>>>

We allow staging annotations around declarations. For example,
\begin{lstlisting}
3`atsigngrnd{`1`
  datatype list = Empty | Cons of int * list
  fun partition (...) = ...
`3`}`1`
fun qsStaged (...) = ...`
\end{lstlisting}
declares the \texttt{list} datatype and \texttt{partition} function at world \bbonep,
by elaborating into:
\begin{lstlisting}
1`val 3`grnd{`Empty3`}` = 3`grnd{`roll (inj ...)3`}`
val 3`grnd{`Cons3`}`  = 3`grnd{`fn (...) => roll (inj ...)3`}`
val 3`grnd{`partition3`}`  = 3`grnd{`fn (...) => ...3`}`
val qsStaged    = fn (...) => ...`
\end{lstlisting}
